On the marginal value of swimming in woodland caribou

### 2021-04-12 paper/manuscript.Rmd
Update manuscript.Rmd

Our focus on forage is due to the limited presence of predators in our system. Throughout their range,
wolves (*Canis lupus*) are the primary predator of caribou, although there are no wolves on the Island
of Newfoundland, predation on adult caribou by coyotes (*Canis latrans*) does occur (Lewis and Mahoney
2014). Within the Fogo Island archipelago, coyotes exist at low density (Huang et al. 2021) and the
probability of occurrence decreases on the smaller islands. The low density of predators throughout
the archipelago is therefore an unlikely driver of swimming in our system, though predation may stillinfluence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).

>>>>

Our focus on forage is due to the limited presence of predators in our system. Throughout their range,
wolves (*Canis lupus*) are the primary predator of caribou, although there are no wolves on the Island
of Newfoundland, predation on adult caribou by coyotes (*Canis latrans*) does occur (Lewis and Mahoney
2014). Within the Fogo Island archipelago, coyotes exist at low density (Huang et al. 2021) and the
probability of occurrence decreases on the smaller islands. The low density of predators throughout
the archipelago is therefore an unlikely driver of swimming in our system, though predation may
still influence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).
